### 2015-12-12 fundamentals/impl.tex
minor correction to the phrasing of the purpose of the modular architecture.

A modular, \acrfull{ABM} approach is ideal for solving the coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies which arise in \Cyclus. Additionally, the choice
to build \Cyclus on open source libraries in modern programming languages
enables both remote and multiprocess execution on a number of platforms. This
section begins by describing the general design features that make \Cyclus both
flexible and powerful: \emph{cluster-ready software} and \emph{dynamically
loadable libraries}.  The
\gls{ABM} framework is then described, focusing on its implementation and benefits
in a fuel cycle context. A discussion of the
time-dependent treatment of discrete resources follows, focusing on the
\gls{DRE}. Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.  Lastly, the methods
for quality assurance are outlined.

>>>>

A modular, \acrfull{ABM} approach is ideal for modeling the coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies which arise in the 
nuclear fuel cycle. Additionally, the choice
to build \Cyclus on open source libraries in modern programming languages
enables both remote and multiprocess execution on a number of platforms. This
section begins by describing the general design features that make \Cyclus both
flexible and powerful: \emph{cluster-ready software} and \emph{dynamically
loadable libraries}.  The
\gls{ABM} framework is then described, focusing on its implementation and benefits
in a fuel cycle context. A discussion of the
time-dependent treatment of discrete resources follows, focusing on the
\gls{DRE}. Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.  Lastly, the methods
for quality assurance are outlined.
